final figures for inclusion

### 2021-04-27 shared analysis files /data_wrangling_plot.Rmd
updates and trying to finalize figures

```{r}
dat_MA_ES %>%
  count(study_id)
```

```{r, echo=FALSE, results = 'hide', message=FALSE}
## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, visreg)
#pacman::p_load(ggsci, plotly,  mgcv)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE,build_vignettes = TRUE)
#library(orchaRd)

@@

```{r}
# keep this to justify range of (-4:5)
dat_MA_ES %>%
filter(yi > -20) %>%
  ggplot(aes(x=yi))+
  geom_histogram(binwidth = 1)
```
**Figure 3.** Contour plot of GAM generated effects sizes overlayed with raw effect sizes from the extracted dataset. Black lines denote the boundary from negative to positive effect sizes. Grey triange denotes excluded contour that lacks any raw data.

@@

```{r}
#plot to include to demonstrate model estimates
full_model_coefficients<- as.data.frame(coef(full_rf_model)) %>%
  tibble::rownames_to_column("covariates")

full_model_coefficients %>%
  ggplot(aes(x = fct_reorder(covariates, coef(full_rf_model)),
             y = coef(full_rf_model),
             fill = coef(full_rf_model) > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = NULL, y = "Coefficient estimate") +
  scale_fill_viridis(discrete = TRUE)+
  theme_bw()
```

@@

```{r, echo= FALSE}
# scatterplot of standardized mean response vs flux range colored and lm fit by org level
ggplot(normalized, aes(x=flux_range, y=yi, color = factor(org_level)))+
  geom_point()+
  labs(title = "SMD across fluctuation ranges colored by organization level and fit with linear model", 
       x = "Temperature fluctuation range (C)",
       y ="SMD",
       color = "Biological organization level")+
  scale_color_viridis(discrete = TRUE, option = "D", labels = c("organismal", "population"))+
  geom_smooth(method="lm", formula = y~x)+
  theme_bw()+
  theme(legend.position="bottom") 
```
**Figure 4.**
We can also see that there a difference in effect size in organization level responses across fluctuation range. Population level reponses trended positively across fluctuation ranges, while organism level responses trended negatively across fluctuation ranges.

>>>>

```{r, echo=FALSE, results = 'hide', message=FALSE}
## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, visreg, forcats)
#pacman::p_load(ggsci, plotly,  mgcv)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE,build_vignettes = TRUE)
#library(orchaRd)

@@

```{r}
# keep this to justify range of (-4:5)
dat_MA_ES %>%
filter(yi > -20) %>%
  ggplot(aes(x=yi))+
  geom_histogram(binwidth = 1)+
  theme_bw()+
  scale_fill_viridis()
```
**Figure 3.** Contour plot of GAM generated effects sizes overlayed with raw effect sizes from the extracted dataset. Black lines denote the boundary from negative to positive effect sizes. Grey triange denotes excluded contour that lacks any raw data.

@@

```{r}
#plot to include to demonstrate model estimates
full_model_coefficients<- as.data.frame(coef(full_rf_model)) %>%
  tibble::rownames_to_column("covariates") %>%
  rename(value = "coef(full_rf_model)") %>%
  arrange(desc(value))

label.df <- data.frame(covariates = c("flux_range", "flux_range:mean_constant_temp", "org_level"),
                       value = c(0.3, -0.01, -0.69))

ggplot(data=full_model_coefficients, aes(x = reorder(covariates, value),
             y = value,
             fill = value > 0)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "Coefficient estimate") +
  scale_fill_viridis(discrete = TRUE)+
  theme_bw()+
  coord_flip()+
  geom_text(data=label.df, label = "*")

p + aes(x= reorder(covariates, value))

@@

```{r, echo= FALSE}
# scatterplot of standardized mean response vs flux range colored and lm fit by org level
ggplot(normalized, aes(x=flux_range, y=yi, color = factor(org_level)))+
  geom_point()+
  labs(title = "SMD across fluctuation ranges colored by organization level and fit with linear model", 
       x = "Temperature fluctuation range (C)",
       y ="SMD",
       color = "Biological organization level")+
  scale_color_viridis(discrete = TRUE, option = "D", labels = c("individual", "population"))+
  geom_smooth(method="lm", formula = y~x)+
  theme_bw()+
  theme(legend.position="bottom") 
```
**Figure 4.**
We can also see that there a difference in effect size in organization level responses across fluctuation range. Population level reponses trended positively across fluctuation ranges, while organism level responses trended negatively across fluctuation ranges.
